Layered Formal Verification of an Industrial TCP/IP Stack

### 2021-05-21 SecDev21/paper.tex
fixing text for  contracts on C interfaced functions

@@

No verification are
performed on the C code, but pre- and postconditions can be attached to
subprograms and they can be called in SPARK code.
The functional specification are not proved, thus it is the role of the
programmer to ensure the correctness of the contracts.

>>>>

Although formal verification can only be applied to the SPARK translated code,  pre- and post-conditions can be attached to C functions interfaced in SPARK to allow reasoning about the side effects of calling these functions by the SPARK code. Since the functional specification of these contracts can not be proved, it is the role of the programmer to ensure their correctnes.

@@
